Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-03-11 paper/rebuttal.txt

We would like to thank all reviewers for their feedback. We will buy an
additional page in the camera ready to enrich the related works section and
improve the text where it was previously cut due to space limitations.
Additional replies:

REVIEW 1

% - novelty
%     - certamente le alternative/sets non sono nuovi; la novita' e' la
%       suddivisione dello spazio di ricerca
%     - cercare roba recente che cita Guo/Bonilla/Viappiani e dimostrare che
%       non esiste nulla di piu' sul punto
%     - diversity in IR esiste [ma non ha lo stesso scopo (non dipende da w)] ma
%       per spazio ci siamo concentrati su related work piu' vicini; si potrebbe
%       comprare una pagina ulteriore nel camera ready per spiegare.
% 
% - set search not analyzed thoroughly
%     - il metodo e' giustificato anche con k=2, che funziona pure bene
%     - k>2 e' utile in base al costo cognitivo; per questo abbiamo messo 2
%       grafici (per query e per iteration); qui si vede il vantaggio di k>2
%     - no messaggio definitivo per via del costo cognitivo e del modello utente;
%       si possono esplorare alternative ma non e' il nostro fuoco; o vederlo
%       come recommendation set (di 5 prendi 1), pero' avvantaggerebbe il nostro
%       metodo
% 
% - *
%     - il fatto che i Bayes siano piu' lenti sono comunque lo stato dell'arte:
%       c'e' un tradeoff tra numero di domande e scalare nel bayesiano; noi
%       invece otteniamo le stesse perf ma scaliamo molto oltre.
%     - gli attributi booleani c'e' un misunderstanding: il problema e' ben
%       piu' complesso. spiegare attributi in dettaglio e quanti bits.

- True, usage of sets of candidates to encourage diversity is not new; the
  novelty is that we exploit the candidates to evenly split the search space.
- Diversity in information retrieval has a different goal, unrelated to
  optimization and learning. We will provide details and further references
  in the additional page.
- Recently the focus in preference elicitation shifted a bit. Our searches in
  the literature found nothing more appropriate than the work of Guo & Sanner,
  and Boutilier. We'd be grateful for any other relevant references.
- The analysis of the setmargin procedure could certaily be more theoretical. XXX
  As proven empirically, the message is that our method can provide close
  better performance than state-of-the-art methods at a fraction of the
  computational cost. This is certainly true for pairwise queries (k=2), while
  for set-based queries, where the cognitive load is less well defined, we
  report both per-iteration and per-query results to cover the full spectrum of
  possibilities.
- Bayesian methods are the state-of-the-art. True, they trade off runtime for
  modelling accuracy. But we do provide comparable performance while scaling
  much more.
- There is a misunderstanding: the number of Boolean attributes in the PC
  dataset is 73, not 8, plus a continuous cost. The problem is much more
  complex than that.

REVIEW 2

% R2
% 
% - citare UTA in OR -> citare UTA quando introduciamo le slacks
% - ha ragione, rephrase (primo qualita', secondo diversita', tutti e due diversita' dei buoni)
% - non normalizzando i pesi (che e' solo una possibilita'), la L1 e' lo standard
%   per sparsificare
% - explain that the linearization trick is used in Boutilier et al. 2006
% - chiarire che il num bool e sum domini; ma i problemi sono tranquilli perche'
%   i w utenti sono semplici e gli XOR restringono il problema
% - why should gamma be crossvalidated? intuition:
%     - il vincolo 2 diversifica
%     - il gamma vuole che gli oggetti siano di buona qualita' che in PE servono
%       perche' l'utente non si incazzi; non e' ovvio quale deve essere il suo
%       contributo percio' crossvalidiamo
%     - chiarire i bump a cosa sono dovuti (non a gamma); tagliato per spazio
% - fix footnote 4 only applies to k=1 (chiarisco che chiariro')
% - explain why 80% sparsity mimics a user (typically cares about 3 or 4 features)
%     - siamo d'accordo che con 3-4 features non serve la sparsita'; peccato
%       che dobbiamo simularlo su poche features (synth) for sake of comparisons
%       perche su PC gli altri metodi non funzionano
%     - la sparsita' non l'abbiamo introdotta per far vedere che il nostro sys
%       va meglio -- l'idea e' che scaliamo meglio sia in sparso che in denso.
%       ma usarla e' ragionevole per modellare l'utente. non ci costa nulla
%       toglierla, e non cambia la sua utilita'. il confronto non e' sulla
%       sparsita' ma sul fatto che gli altri non scalano)
%       (infatti la scalabilita' e' il nostro cavallo di battaglia)

- Thanks for the reference, it will be integrated.
- Correct, <wi,xi> encourages the quality of the xi's, diversity is given
  by constraint 2. We will rephrase the sentence.
- Fixing the 1-norm is not the only option. In our case, the norm is variable
  and sparsity is encouraged via LASSO. This is a rather standard approach.
- We will clarify that the linearization trick is taken from elsewhere, and
  refer to the paper by Boutilier et al.
- We plan to extend the work to real variables, as per the Conclusion;
  but this is beyond the scope of this paper.
- User resources strongly limit the overall complexity of the MILP problem.
  Current MILP solvers can easily deal with problems of this magnitude.
- Indeed linearly dependent variables are not very expressive. We are
  interested in extensions to hybrid Boolean/continuous domains, as per the
  Conclusion, and currently investigating two directions: alternating between
  optimization of Boolean and continuous variables, and leveraging non-linear
  solvers.
- Gamma controls the importance of candidate item quality for diversity;
  gamma=0 could be used. Since the correlation is not known beforehand, we
  include gamma in the cross-validation.
- Footnote 4 only applies to k=1 (as constraint 2 vanishes). Will fix.
- NOT SURE HOW TO WRITE IT DOWN

REVIEW 3

% - citeremo e commenteremo, grazie
% - margin must be non-negative, make clearer

- Thanks for the references, we will make sure to include them.
- The margin must be non-negative, as specified in the text above Eq 1; we will
  point it out more clearly.

REVIEW 4

% - BT: forse ci favorisce, ci stiamo solo confrontando con quello che fanno gli
%   altri, preso dai competitors; al contrario, sono i modelli bayesiani che
%   lo sfruttano meglio (o almeno che potrebbero)
% - cognitive load: ha ragione, ma tutti fanno domande a coppie es Guo & Sanner,
%   ci accodiamo. non e' chiaro come formalizzare (chiedere agli psicologi)? e'
%   da investigare. in effetti e' quello che vogliamo fare (trovare query che
%   sono piu' facili per l'utente). ma va oltre lo scopo.
% - scalability: stiamo sempre parlando di interazione con l'utente, quindi siamo
%   lontani dal raggiugnere la complex gestibile da un MILP solver. il PC ad es
%   e' gestibile mentre per l'utente e' complesso (non si va sulle migliaia di
%   var booleane). capire quanti Bools un MILP gestisce (chiedere a Roberto?).
%   la sat del solver sta molto sopra la sat dell'utente.
% - reals: future work di sicuro, infatti l'abbiamo messo li' -- le estensioni
%   sarebbero non-lineari per via di <w,x>, citare ultimo paper sanner. in
%   realta' ongoing su hybrid (alternated o nonlinear).

- We do not think the BT response model favors our method. First, it was
  previously used to evaluate the competitors, we merely took it from there.
  Second, given that Bayesian models are tied to the response model, they are
  more likely to benefit from the additional constraints that the modelling
  provides.
- True, modelling the cognitive load is not easy. We have ongoing work to
  explore this issue further, in collaboration with psychologists. In the
  paper we just followed the common practice of pairwise queries, for
  comparability.
- User resources strongly limit the overall complexity of the MILP problem;
  MILP solvers are well-equipped to solve problems of this magnitude.
- Indeed linearly dependent variables are not very expressive. We are very much
  interested in extending the method to hybrid Boolean/continuous domains, as
  hinted to in the Conclusion. We are currently investigating two directions:
  alternating between optimization of Boolean and continuous variables, and
  leveraging non-linear solvers.
- Thanks for the reference, we'll make sure to include it.

### 2016-03-11 paper/rebuttal.txt

We would like to thank all reviewers for their feedback. We will buy an
additional page for the camera ready to enrich the related works section and
improve the text where it was previously cut due to space limitations.
Additional replies:

@@

REVIEW 1

% - novelty
%     - certamente le alternative/sets non sono nuovi; la novita' e' la
%       suddivisione dello spazio di ricerca
%     - cercare roba recente che cita Guo/Bonilla/Viappiani e dimostrare che
%       non esiste nulla di piu' sul punto
%     - diversity in IR esiste [ma non ha lo stesso scopo (non dipende da w)] ma
%       per spazio ci siamo concentrati su related work piu' vicini; si potrebbe
%       comprare una pagina ulteriore nel camera ready per spiegare.
% 
% - set search not analyzed thoroughly
%     - il metodo e' giustificato anche con k=2, che funziona pure bene
%     - k>2 e' utile in base al costo cognitivo; per questo abbiamo messo 2
%       grafici (per query e per iteration); qui si vede il vantaggio di k>2
%     - no messaggio definitivo per via del costo cognitivo e del modello utente;
%       si possono esplorare alternative ma non e' il nostro fuoco; o vederlo
%       come recommendation set (di 5 prendi 1), pero' avvantaggerebbe il nostro
%       metodo
% 
% - *
%     - il fatto che i Bayes siano piu' lenti sono comunque lo stato dell'arte:
%       c'e' un tradeoff tra numero di domande e scalare nel bayesiano; noi
%       invece otteniamo le stesse perf ma scaliamo molto oltre.
%     - gli attributi booleani c'e' un misunderstanding: il problema e' ben
%       piu' complesso. spiegare attributi in dettaglio e quanti bits.

- True, usage of sets of candidates to encourage diversity is not new; the
  novelty is that we exploit the candidates to rationally split the search space.
- Diversity in information retrieval has a different goal, unrelated to
  optimization and learning. We will provide details and further references
  in the additional page.
- Recently the focus in preference elicitation shifted a bit. Our searches in
  the literature found nothing more appropriate than the work of Guo & Sanner,
  and Boutilier. We'd be grateful for any other relevant references.
- The analysis of the setmargin procedure could certainly be more theoretical. XXX
  As proven empirically, the message is that our method can provide close
  better performance than state-of-the-art methods at a fraction of the
  computational cost. This is certainly true for pairwise queries (k=2), while
  for set-based queries, where the cognitive load is less well defined, we
  report both per-iteration and per-query results to cover the full spectrum of
  possibilities.
- Bayesian methods are the state-of-the-art. True, they trade off runtime for
  modelling expressivity. But we do provide comparable performance while
  scaling much more.
- There is a misunderstanding. The task is more complex than perceived by
  the reviewer: the number of Boolean attributes in the PC dataset is 73, not
  8.

@@

REVIEW 2

% R2
% 
% - citare UTA in OR -> citare UTA quando introduciamo le slacks
% - ha ragione, rephrase (primo qualita', secondo diversita', tutti e due diversita' dei buoni)
% - non normalizzando i pesi (che e' solo una possibilita'), la L1 e' lo standard
%   per sparsificare
% - explain that the linearization trick is used in Boutilier et al. 2006
% - chiarire che il num bool e sum domini; ma i problemi sono tranquilli perche'
%   i w utenti sono semplici e gli XOR restringono il problema
% - why should gamma be crossvalidated? intuition:
%     - il vincolo 2 diversifica
%     - il gamma vuole che gli oggetti siano di buona qualita' che in PE servono
%       perche' l'utente non si incazzi; non e' ovvio quale deve essere il suo
%       contributo percio' crossvalidiamo
%     - chiarire i bump a cosa sono dovuti (non a gamma); tagliato per spazio
% - fix footnote 4 only applies to k=1 (chiarisco che chiariro')
% - explain why 80% sparsity mimics a user (typically cares about 3 or 4 features)
%     - siamo d'accordo che con 3-4 features non serve la sparsita'; peccato
%       che dobbiamo simularlo su poche features (synth) for sake of comparisons
%       perche su PC gli altri metodi non funzionano
%     - la sparsita' non l'abbiamo introdotta per far vedere che il nostro sys
%       va meglio -- l'idea e' che scaliamo meglio sia in sparso che in denso.
%       ma usarla e' ragionevole per modellare l'utente. non ci costa nulla
%       toglierla, e non cambia la sua utilita'. il confronto non e' sulla
%       sparsita' ma sul fatto che gli altri non scalano)
%       (infatti la scalabilita' e' il nostro cavallo di battaglia)

- Thanks for the reference, it will be integrated.
- Correct, <wi,xi> encourages the quality of the xi's, diversity is given
  by constraint 2. We will rephrase the sentence.
- Fixing the 1-norm is not the only option. In our case, the norm is variable
  and sparsity is encouraged through LASSO. This is a standard approach.
- We will clarify that the linearization trick is taken from elsewhere, and
  refer to the paper by Boutilier.
- We plan to extend the work to real variables, as per the Conclusion;
  but this is beyond the scope of this paper.
- User resources strongly limit the overall complexity of the MILP problem.
  Current MILP solvers can easily deal with problems of this magnitude.
- Gamma controls the importance of candidate item quality for ensuring
  diversity; gamma=0 could be used. Since the correlation is not known
  beforehand, we include gamma in the cross-validation.
- Footnote 4 should only apply to k=1 (as constraint 2 vanishes. Will fix.
- NOT SURE HOW TO WRITE IT DOWN

### 2016-03-11 paper/ijcai16.tex
paper: typo.

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first
experiment we evaluate the behavior of the proposed method in an
artificial setting with increasingly complex problems. We developed
synthetic datasets with $r$ attributes, for increasing values of $r$.
Each attribute takes one of $r$ possible values, so that the one-hot
encoding of attributes results in $m=r^2$ features. In terms of space
of configurations, for $r=3$ the synthetic dataset corresponds to 
$\calX_\text{feasible} = [3] \times [3] \times [3]$, for $r=4$ to
$\calX_\text{feasible} = [4] \times [4] \times [4] \times [4]$, and so on. The
cardinality of $\calX_\text{feasible}$ is $r^r$, and grows (super)
exponentially with $r$.
% We developed
% seven synthetic datasets: each dataset involves $m=2,\ldots,7$
% attributes, where each attribute takes one of $m$ possible
% values. More explicitly, for $m=2$ the synthetic dataset is
% $\calX_\text{feasible} = [2] \times [2]$, for $m=3$ to
% $\calX_\text{feasible} = [3] \times [3] \times [3]$, and so on. The
% cardinality of $\calX_\text{feasible}$ is $m^m$, and grows (super)
% exponentially with $m$. 
For $r=3$, the dataset is comparable in size to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal}.
%, which have
%three attributes with 2, 2 and 5 values respectively, for a total of
%20 feasible configurations.  
For larger $r$ the size of the space grows much larger than the one
typically used in the Bayesian preference elicitation literature, and
as such represents a good testbed for comparing the scalability of the
various methods. The feasible configuration space was encoded in {\sc
  SetMargin} through appropriate MILP constraints, while the other
methods require all datasets to be explicitly grounded.  Users were
simulated by drawing $20$ random utility vectors from each of four
different distributions. The first two mimic those used
in~\cite{guo2010real}\footnote{We used the parameters implemented in their code, which are slightly different from those reported in the paper.}%
%\footnote{The normal distribution reported
%  in~\cite{guo2010real} differs slightly from the one implemented in
%  the code of their experimental setting.  In our experiments we use
%  the latter.}
: (1) a uniform distribution over $[1, 100]$ for each
individual weight, and (2) a normal distribution with mean $25$
and %covariance
standard deviation $\frac{25}{3}$ (each attribute is sampled i.i.d).
We further produced two novel {\em sparse} versions of the uniform and
normal distributions setting to zero $80\%$ of the entries (sampled
uniformly at random). We set a maximum budget of 100 iterations for all
methods for simplicity.

>>>>

\paragraph{Synthetic Dataset.} Following the experimental protocol
in~\cite{guo2010real} and \cite{viappiani2010optimal}, in the first
experiment we evaluate the behavior of the proposed method in an
artificial setting with increasingly complex problems. We developed
synthetic datasets with $r$ attributes, for increasing values of $r$.
Each attribute takes one of $r$ possible values, so that the one-hot
encoding of attributes results in $m=r^2$ features. In terms of space
of configurations, for $r=3$ the synthetic dataset corresponds to 
$\calX_\text{feasible} = [3] \times [3] \times [3]$, for $r=4$ to
$\calX_\text{feasible} = [4] \times [4] \times [4] \times [4]$, and so on. The
cardinality of $\calX_\text{feasible}$ is $r^r$, and grows (super)
exponentially with $r$.
% We developed
% seven synthetic datasets: each dataset involves $m=2,\ldots,7$
% attributes, where each attribute takes one of $m$ possible
% values. More explicitly, for $m=2$ the synthetic dataset is
% $\calX_\text{feasible} = [2] \times [2]$, for $m=3$ to
% $\calX_\text{feasible} = [3] \times [3] \times [3]$, and so on. The
% cardinality of $\calX_\text{feasible}$ is $m^m$, and grows (super)
% exponentially with $m$. 
For $r=3$, the dataset is comparable in size to the synthetic one used
in~\cite{guo2010real} and~\cite{viappiani2010optimal}.
%, which have
%three attributes with 2, 2 and 5 values respectively, for a total of
%20 feasible configurations.  
For larger $r$ the size of the space grows much larger than the ones
typically used in the Bayesian preference elicitation literature, and
as such represents a good testbed for comparing the scalability of the
various methods. The feasible configuration space was encoded in {\sc
  SetMargin} through appropriate MILP constraints, while the other
methods require all datasets to be explicitly grounded.  Users were
simulated by drawing $20$ random utility vectors from each of four
different distributions. The first two mimic those used
in~\cite{guo2010real}\footnote{We used the parameters implemented in their code, which are slightly different from those reported in the paper.}%
%\footnote{The normal distribution reported
%  in~\cite{guo2010real} differs slightly from the one implemented in
%  the code of their experimental setting.  In our experiments we use
%  the latter.}
: (1) a uniform distribution over $[1, 100]$ for each
individual weight, and (2) a normal distribution with mean $25$
and %covariance
standard deviation $\frac{25}{3}$ (each attribute is sampled i.i.d).
We further produced two novel {\em sparse} versions of the uniform and
normal distributions setting to zero $80\%$ of the entries (sampled
uniformly at random). We set a maximum budget of 100 iterations for all
methods for simplicity.
